---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)

# Set ggplot theme
thm <- ggplot2::theme_bw(base_size = 11, base_family = "") +
  ggplot2::theme(
    panel.background  = element_rect(fill = "transparent", colour = NA),
    plot.background   = element_rect(fill = "transparent", colour = NA),
    legend.position   = "top",
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.key        = element_rect(fill = "transparent", colour = NA),
    plot.title        = element_text(hjust = 0.5, size = ggplot2::rel(1.5))
  )
theme_set(thm)

# COVID data ----
covid_data <- readr::read_csv("data/covid19_case_summary_2020-04-28.csv")
state_data <- dplyr::filter(covid_data, attribute == "Statewide") %>% 
  dplyr::select(Metric = metric, number = value)
cur_date <- covid_data$attribute %>% 
  grep("^2020-[0-9]{2}-[0-9]{2}", ., value = TRUE) %>% 
  sort(decreasing = TRUE) %>% 
  head(1) %>% 
  strptime(format = "%Y-%m-%d", tz = "MST") %>% 
  format("%B %d, %Y")

# badges ----
badge_style <- "flat-square"
logo        <- "appveyor"
n_cases <- pull(filter(state_data, Metric == "Cases"), number)
cases <- sprintf("https://img.shields.io/badge/Cases-%i-%s.svg?style=%s&logo=%s",
                 n_cases, "success", badge_style, logo)
value  <- dplyr::pull(filter(state_data, Metric == "People Tested"), number)
tested <- sprintf("https://img.shields.io/badge/People_Tested-%i-%s.svg?style=%s&logo=%s",
                 value, "success", badge_style, logo)
pct_pos <- sprintf("https://img.shields.io/badge/Case_Rate-%0.1f%%25-%s.svg?style=%s&logo=%s",
                 n_cases / value * 100, "success", badge_style, logo)
value  <- filter(state_data, Metric == "Deaths") %>% dplyr::pull(number)
deaths <- sprintf("https://img.shields.io/badge/Deaths-%i-%s.svg?style=%s&logo=%s",
                  value, "success", badge_style, logo)
value    <- filter(state_data, Metric == "Counties") %>% pull(number)
counties <- sprintf("https://img.shields.io/badge/Counties-%i-%s.svg?style=%s&logo=%s", 
                    value, "success", badge_style, logo)
value <- filter(state_data, Metric == "Hospitalizations") %>% dplyr::pull(number)
hospitalizations <- sprintf("https://img.shields.io/badge/Hospitalizations-%i-%s.svg?style=%s&logo=%s",
                 value, "success", badge_style, logo)

```


# Outbreak Summary 
### `r cur_date`

![cases](`r cases`)
![tested](`r tested`)
![pct_pos](`r pct_pos`)
![deaths](`r deaths`)
![counties](`r counties`)
![hospitalization](`r hospitalizations`)



### [stufield.github.io/COVID-19](https://stufield.github.io/COVID-19)




# COVID-19 Pandemic - Colorado

This page highlights the `COVID-19` cases in Colorado both 
through time and by county (CO has 64 counties).

Data is obtained from the Colorado Department of Public Health & Environment 
(CDPHE).

See the `CDPHE` [website](https://covid19.colorado.gov/case-data) for more 
information and raw case data.

----------

## Summary
```{r summary, echo = FALSE}
knitr::kable(state_data)
```

## Cases by Sex
```{r sex_data, echo = FALSE}
dplyr::filter(covid_data, description == "COVID-19 in Colorado by Sex" &
                metric == "Percent of Cases") %>% 
  dplyr::select(Sex = attribute, Percent = value) %>%  
  dplyr::mutate(Percent = sprintf("%0.2f%%", Percent)) %>% 
  knitr::kable()
```

## Cases by Age
```{r age_data, fig.width=10, fig.height=5}
covid_data %>%
  dplyr::filter(
    description == "Cases of COVID-19 Reported in Colorado by Age Group, Hospitalization, and Outcome" &
      !is.na(value)) %>% 
  tidyr::separate(attribute, into = c("Age", "Outcome"), sep = ", ") %>%
  dplyr::select(Age, Outcome, Cases = value) %>%
  ggplot(aes(x = Age, y = Cases, group = Outcome)) +
  geom_bar(stat = "identity", aes(fill = Outcome)) +
  ggtitle("Case Proportion by Age & Outcome")
```

## COVID-19 Cases by County
```{r county, fig.width=10, fig.height=5}
covid_data %>%
  dplyr::filter(description == "Colorado Case Counts by County" & metric == "Cases") %>%
  dplyr::mutate(County = stringr::str_remove(attribute, " County$")) %>%
  dplyr::filter(County !=  "Grand Total") %>%
  ggplot(aes(y = value, x = reorder(County, -value))) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Cases", title = "Colorado Cases by County", x = "County")
```

## COVID-19 Cases Over Time
```{r time, fig.width=10, fig.height=5}
time_data <- covid_data %>% 
  dplyr::filter(
    description == "Cases of COVID-19 in Colorado by Date Reported to the State" & 
      !is.na(value)) %>% 
  dplyr::mutate(
    date = as.Date(trunc(strptime(attribute, format = "%Y-%m-%d", tz = "MST"), "day")),
    total = cumsum(value)
  )
time_data %>%
  ggplot(aes(x = date, y = value)) +
  geom_point(size = 2) +
  geom_smooth(method = "loess", se = FALSE) +
  scale_x_date(breaks = time_data$date) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Cases", title = "Colorado Cases by Date", x = "")
```

-------------

Created by [Rmarkdown](https://github.com/rstudio/rmarkdown)
(v`r utils::packageVersion("rmarkdown")`) and `r R.version$version.string`.
