---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
data <- readr::read_csv("data/covid19_case_summary_2020-03-27.csv")
county_data <- data %>%
  dplyr::filter(description == "Case Counts by County" & metric == "Cases") %>%
  dplyr::mutate(County = stringr::str_remove(attribute, " County$")) %>%
  dplyr::filter(County !=  "Grand Total")
time_data <- dplyr::filter(data, grepl("^2020", attribute)) %>%
  dplyr::mutate(
    date = as.Date(trunc(strptime(attribute, format = "%Y-%m-%d", tz = "MST"), "day"))
  )
```

# COVID-19 Pandemic - Colorado Edition

This page highlights the `COVID-19` cases in Colorado both 
through time and by county (CO has 64 counties).

Data is obtained from the Colorado Department of Public Health & Environment 
(CDPHE).

See the `CDPHE` [website](https://covid19.colorado.gov/case-data) for more information.


## COVID-19 Cases by County
```{r county, fig.width=10, fig.height=5}
county_data %>%
  ggplot(aes(y = value, x = County)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Cases", title = "Colorado Cases by County")
```

## COVID-19 Cases Over Time
```{r time, fig.width=10, fig.height=5}
time_data %>%
  ggplot(aes(x = date, y = value)) +
  geom_point(size = 2) +
  geom_smooth(method = "loess", se = FALSE) +
  ggplot2::scale_x_date(breaks = time_data$date) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Cases", title = "Colorado Cases by Date")
```

-------------

Created by [Rmarkdown](https://github.com/rstudio/rmarkdown)
(v`r utils::packageVersion("rmarkdown")`) and `r R.version$version.string`.
